---
title: "linear_models_1"
author: "Hana Akbarnejad"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}

data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

** price as an outcome that may depend on rating and borough.**

## fit the first linear model
```{r}

fit = lm(price ~ stars + boro, data = nyc_airbnb)
```
If I have not specify my factor orders, it will assume categorically and chooses the reference according to that! (btonx)

```{r}
fit

summary(fit)

coef(fit) #extracting coefficients

summary(fit)$coef
```

tidy the results instead!:
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")
  ) %>% 
  knitr::kable(digits = 3)
```

## take a look at factors:
```{r}

nyc_airbnb = nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```

## now if we fit, we'll have different output! because our reference has been manipulated by changing the factors.
```{r}

fit = lm(price ~ stars + boro, data = nyc_airbnb)

summary(fit)

# can use glance instead of tidy in broom::
fit %>% 
  broom::glance()  #p_value here is not very useful because it is global, but p_value in broom::tidy is pairwise and useful!
```


## Diagnostics! >>> ALL ABOUT RESIDUALS
```{r}

modelr::add_residuals(nyc_airbnb, fit)  #adding residuals to my model

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_violin() +
  ylim(-500, 500)

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()
```

## fitted values (predicted values)
```{r}

modelr::add_predictions(nyc_airbnb, fit)
```

## nesting
We love nesting! <3

```{r}
fit_interaction = lm(price ~ stars * boro + room_type * boro, data = nyc_airbnb)  # * gives ud interaction!

nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm (price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

# try mapping!!!
```{r}

nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map (models, broom::tidy)
  ) %>% 
  select(boro, results) %>% 
  unnest(results)
```

# let's nest neighborhoods
```{r}

manhattan_nested_lm = nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map (models, broom::tidy)
  ) %>% 
  select(neighborhood, results) %>% 
  unnest(results)
```

## plotting nested stuff!
```{r}

manhattan_nested_lm %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```
They are all negative which means it generally costs you less if you go to a private room instead of whole house/apartment.

nesting is not the answer to all questions!

we can fit things with binary outcomes instead of continuous outcomes. using binomial. for example, homicide cases as resolved/not resolves! look at the course website.